\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{GNANADEEP GUTLAPALLI} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+(91) 8897815879 \\ New Bowepally, Hyderabad} 
\address{\href{mailto:gnanadeepchowdhary@gmail.com}{G-Mail} \\ \href{https://gnanadeep1.github.io/my-portfolio/}{Portfolio} \\ \href{https://github.com/Gnanadeep1}{GitHub}}  %

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Bachelor of Technology}, Computer Science \& Engineering\-  (AI\&ML) \hfill {2021 - 2025}\\
CMR College Of Engineering \& Technology\\
CGPA:8.56(Present)

{\bf Board Of Intermediate Education (MPC)},Telangana \hfill {2019 - 2021}\\
Sri Chaitanya Junior College \\
Percentage:87

{\bf  High School},Telangana \hfill {2018 - 2019}\\
Sri Chaitanya School \\
GPA:9.7

%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages & C, C++, Java, Python
\\
Web Development & HTML, CSS, JavaScript
\\
Frameworks & Node JS, Express JS,React JS\\
Databases & MySQL,Mongo DB\\
Machine Learning & Numpy, Pandas\\
IOT Technologies & Working with dc motors, different sensors, relay module, basic code and connections.

\end{tabular}\\
\end{rSection}

\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{Note Pad Application. }Built using HTML, CSS, and JavaScript stores notes in the browser's local storage, ensuring data persistence without a server. It offers a simple, intuitive interface for creating, editing, and managing notes.  { \href{https://gnanadeep1.github.io/Note-Site/}{(Click Here)}}
\item \textbf{Smart Public Tap. } {A smart public tap uses sensors and internet technology to manage water use efficiently.It spots leaks, and can be controlled remotely. The tap also works without touching, making it more hygienic.}

\end{rSection} 

%----------------------------------------------------------------------------------------
\begin{rSection}{ACHIEVEMENTS} 
 \begin{itemize}
     \item Finalist in Code King, a National Level Technical Symposium organized by Jawaharlal Nehru Technological
University (JNTU).
    \item  I am good at solving lots of different problems on different websites. I've shown I can solve problems by fixing lots of different coding tasks. I'm really good at solving problems on different websites.
    \begin{itemize}
        \item \textbf{}{ \href{https://leetcode.com/u/21h51a6694/}{LeetCode}}
 \item \textbf{}{ \href{https://codeforces.com/profile/gnanadeepchowdhary}{Codeforces}}
 \item \textbf{}{ \href{https://www.codechef.com/users/gdgdd_123455#=}{CodeChef}}
 \end{itemize}{}
    \end{itemize}





\end{rSection}




\end{document}
